---
title: "curso de formação em R e git"
author: "Andrea Sánchez-Tapia, Sara Mortara, Diogo Rocha"
date: "28/01/2020"
fontsize: 14pt
output: 
  beamer_presentation:
    latex_engine: xelatex 
    incremental: true
    template:
    
header-includes:
  - \usepackage{longtable,booktabs}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{xcolor}
  - \usepackage{subfig}
  - \usepackage{fontspec}
  - \usefonttheme{professionalfonts} 
  - \usefonttheme{serif} 
  - \setmainfont{Roboto Condensed}
  - \definecolor{cor1}{HTML}{A70000}
  - \definecolor{cor2}{HTML}{1C1C19} 
  - \definecolor{cor3}{HTML}{ff0000}
  - \setbeamercolor{title}{fg = cor1}
  - \setbeamercolor{frametitle}{fg = cor1}
  - \setbeamercolor{structure}{fg = cor2}
  - \renewcommand\alert[1]{\textcolor{cor3}{#1}}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. \alert{Markdown} is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

